Delocalization of Eigenvectors in Random Matrices

### 2025-03-21 Draft.tex
error diagram bound

\end{tikzpicture}
\end{center}
In order to complete the latter result, we need to consider two subcases w.r.t. to the double lines by splitting the double line $\left[\{\text{Id} + (t-s)\Theta_t\}S^{1/2}\right]_{yb}$ into its two components:
\begin{itemize}
\item $(t-s)\left[\Theta_t\right]_{yb} \lesssim (t-s)W^{-1}\eta_t^{-1/2}\lesssim W^{-1}\eta_t^{-1/2}\eta_s$ (estimate 3 \& 7), where by summing over $y$ with estimate 1, we get $O(W^{1/2}\eta_s^{-3/4})$  over $x$ with estimate 6, we have $O(\eta_t^{-1}\eta_s)$, we get a combined term $O(W^{-1/2}\eta_t^{-3/2}\eta_s^{5/4})$
\item $\text{Id}_{yb}$ is of course $O(1)$, hence we don't have a varying term, which means that we can bound the edge ending at $y$ with estimate 2, s.t. we get $O(W^{-1/2}\eta_s^{-1/4})$ term. Combining it with $O(\eta_t^{-1}\eta_s)$ from estimate 6, we have $O(W^{-1/2}\eta_t^{-1}\eta_s^{3/4})$. With this we achieve a total bound: 
\end{itemize}
$$\max_{i=1, \cdots, 4}\left\vert\mathcal{G}_{i0, s}\right\vert\lesssim W^{-2}\eta_t^{-3/2}+W^{-2}\eta_t^{-1}\eta_s^{-1/2}$$
Lastly, we need to integrate over $s\in [0, 5]$ by using a change of variable $\sigma =\eta_s$, s.t. the bounds of the integral are then $\sigma\in [\eta_t, O(1)]$, i.e we have:
$$\max \int_0^t|\mathcal{G}_{i0, s}|ds\lesssim W^{-2}\eta_t^{-3/2} \int_{\eta_t}^{O(1)}d\sigma + W^{-2}\eta_t^{-1}\int_{\eta_t}^{O(1)}\sigma^{-1/2}d\sigma \lesssim$$
$$\lesssim W^{-2}\eta_t^{-3/2}-W^{-2}\eta_t^{-1/2}+2N^{-2}\eta_t^{-1}-2W^{-2}\eta_t^{-1/2}\lesssim W^{-2}\eta_t^{-3/2} $$

>>>>

\end{tikzpicture}
\end{center}
In order to complete the latter result, we need to consider two subcases w.r.t. to the double lines by splitting the double line $\left[\{\text{Id} + (t-s)\Theta_t\}S^{1/2}\right]_{yb}$ into its two components:
\begin{itemize}
\item $(t-s)\left[\Theta_t\right]_{yb} \lesssim (t-s)W^{-1}\eta_t^{-1/2}\lesssim W^{-1}\eta_t^{-1/2}\eta_s$ (estimate 3 \& 7), where by summing over $y$ with estimate $(1)$, we get $ O(W^{3\delta_\sto/20}W^{\frac{1}{2}+\epsilon}\eta_s^{-3/4})$  over $x$ with estimate $(6)$, we have $O(\eta_t^{-1}\eta_s)$, we get a combined term $O((t-s) W^{\delta_\sto/20}W^{-\frac{1}{2}+\epsilon}\eta_t^{-3/2}\eta_s^{1/4})$
\item $\text{Id}_{yb}$ is of course $O(1)$, hence we don't have a varying term. This means that we can bound the edge ending at $y$ with estimate $(2)$, s.t. we get $O( W^{2\delta_\sto/20}W^{-1/2}\eta_s^{-1/4})$ term. Combining it with $O(\eta_t^{-1}\eta_s)$ from estimate $(6)$, we have $O( W^{\delta_\sto/20}W^{-1/2}\eta_t^{-1}\eta_s^{3/4})$. With this, the total bound is: 
\end{itemize}

\begin{center}
\begin{tikzpicture}[
    thick, % Line thickness
    wavy/.style={decorate, decoration={snake, amplitude=2pt, segment length=5pt}},
    ]
\node (a) at (0,0) {a};
\node (x) at (1, 0) {x};
\node (y) at (2, 0) {y};
\node (b) at (3, 0) {b};

\end{tikzpicture}
$\lesssim  (t-s) W^{\delta_\sto/20}W^{-\frac{1}{2}+\epsilon}\eta_t^{-3/2}\eta_s^{1/4} + W^{\delta_\sto/20}W^{-1/2}\eta_t^{-1}\eta_s^{3/4}\lesssim$
\end{center}
$$\lesssim W^{\delta_\sto/20}W^{-\frac{1}{2}+\epsilon}\eta_t^{-3/2}\eta_s^{5/4} + W^{\delta_\sto/20}W^{-1/2}\eta_t^{-1}\eta_s^{3/4}$$
Lastly, we need to integrate over $s\in [0, t]$ by using a change of variable $\sigma =\eta_s$, s.t. the bounds of the integral are then $\sigma\in [\eta_t, O(1)]$, i.e we have:
$$\max_{i=1, 2, 3, 4} \int_0^{t\wedge \tau_\sto}|\mathcal{G}_{i0, s}|ds\lesssim W^{-2}\eta_t^{-3/2} \int_{\eta_t}^{O(1)}d\sigma + W^{-2}\eta_t^{-1}\int_{\eta_t}^{O(1)}\sigma^{-1/2}d\sigma \lesssim$$
$$\lesssim W^{-2}\eta_t^{-3/2}-W^{-2}\eta_t^{-1/2}+2N^{-2}\eta_t^{-1}-2W^{-2}\eta_t^{-1/2}\lesssim W^{-2}\eta_t^{-3/2} $$
